Causes and effects in Dichotomous Comparative Judgments: an information-theoretical system of plausible mechanism

### 2024-10-16 _tex/index.tex
Built site for gh-pages

Over the past decade, numerous studies have documented the effectiveness
of the \emph{comparative judgment} (CJ) method
\citep{Thurstone_1927, Pollitt_2012a} for assessing competencies and
traits. These studies have examined the method's strengths from two main
perspectives: its capacity to produce reliable and valid trait scores,
and its practical applicability. In terms of reliability and validity,
research indicates that CJ generates precise and consistent scores that
accurately represent the traits being measured. Key contributions in
this area include those by \citet{Bramley_2008}, \citet{Pollitt_2012b},
\citet{Whitehouse_2012}, \citet{Lesterhuis_2018},
\citet{vanDaal_et_al_2019}, \citet{Bramley_et_al_2019},
\citet{Verhavert_et_al_2019}, \citet{Crompvoets_et_al_2022}, and
\citet{Bouwer_et_al_2023}. Regarding practical applicability, several
studies have demonstrated the method's versatility in both educational
and non-educational settings, offering an efficient and effective
alternative for measurement and evaluation. Notable examples include the
works of \citet{Jones_2015}, \citet{Bartholomew_et_al_2018},
\citet{Jones_et_al_2019}, \citet{Marshall_et_al_2020},
\citet{Bartholomew_et_al_2020}, and \citet{Boonen_et_al_2020}.

@@

>>>>

Over the past decade, numerous studies have documented the effectiveness
of the \emph{comparative judgment} (CJ) method
\citep{Thurstone_1927, Pollitt_2012a} for assessing competencies and
traits. These studies have evaluated CJ from two main perspectives: its
ability to produce reliable and valid trait scores, and its practical
applicability. In terms of reliability and validity, research has shown
that CJ can generate precise and consistent scores that accurately
represent the traits being measured. Notable contributions in this
research area include studies by \citet{Pollitt_2012b},
\citet{Whitehouse_2012}, \citet{vanDaal_et_al_2016},
\citet{Lesterhuis_2018}, \citet{vanDaal_et_al_2019},
\citet{Bramley_et_al_2019}, \citet{Verhavert_et_al_2019},
\citet{Crompvoets_et_al_2022}, and \citet{Bouwer_et_al_2023}. Regarding
practical applicability, several studies have highlighted the method's
versatility in both educational and non-educational contexts, presenting
it as an efficient and effective alternative for measurement and
evaluation. Key examples in this research area include the works of
\citet{Jones_2015}, \citet{Bartholomew_et_al_2018},
\citet{Jones_et_al_2019}, \citet{Marshall_et_al_2020},
\citet{Bartholomew_et_al_2020}, and \citet{Boonen_et_al_2020}.

Nevertheless, despite the growing number of CJ studies, the research
approaches employed in the literature have been unsystematic and
non-integrated, leading to the oversight of several critical issues
related to the method. These issues include concerns about the
measurement model responsible for generating the CJ scores, the
structural component used for further data analysis and hypothesis
testing, and challenges related to the design of CJ experiments. For
instance, a notable concern regarding the measurement model is the
prevalent reliance on the assumptions of Case 5 from Thurstone's law of
comparative judgment \citeyearpar{Thurstone_1927}. Although Case 5 was
originally articulated to produce a ``rough measurement'' or ``rather
coarse scaling'' of traits \citep[p.~268-269]{Thurstone_1927}, its
assumptions have become predominant in the literature due to its
implementation through the Bradley-Terry-Luce (BTL) model
\citep{Bradley_et_al_1952, Luce_1959}. This leaves issues such as the
presence of judge' biases hinted by \citet{Bramley_2008} and
\citet{Kelly_et_al_2022}, and evidenced by \citet{Pollitt_et_al_2003},
\citet{Arlett_2003}, and \citet{Guthrie_2003}

@@

\subsection{Let's talk about Thurstone co.}\label{sec-theory-thurstone}
